Exploring probability distributions for bivariate temporal granularities

### 2019-09-13 main.Rmd
adding all harmonies in cricket example

# change all of these to gravitas function
VIC <- read.csv("VIC2015/Data/demand_VIC.csv")
VIC$Date <- as.Date(VIC$Date, origin = "1899-12-30")

@@

```{r hierarchy, echo=TRUE}
hierarchy_model <- tibble::tibble(units = c("index", "ball", "over", "inning", "match"), convert_fct = c(1, 6, 20, 2, 1))
hierarchy_model
```

@@

```{r read_data, echo=TRUE}

@@

cricket_tsibble %>% dynamic_create_gran(
  "ball_over",
  hierarchy_model
)

cricket_tsibble %>% granplot("ball_over", "inning_match",
  hierarchy_model,
  response = "total_runs",
  plot_type = "boxplot"
)

cricket_tsibble %>% granplot("over_inning",
  "inning_match",
  hierarchy_model,
  response = "total_runs",
  plot_type = "quantile"
)

cricket_tsibble %>%
  dynamic_create_gran(
    "over_inning",
    hierarchy_model
  ) %>%
  dynamic_create_gran(
    "inning_match",
    hierarchy_model
  ) %>%
  granplot(
    gran1 = "inning_match",
    gran2 = "over_inning",
    hierarchy_model,
    response = "total_runs",
    plot_type = "quantile"
  )

cricket_tsibble %>%
  dynamic_create_gran(
    "ball_over",
    hierarchy_model
  ) %>%
  dynamic_create_gran(
    "over_match",
    hierarchy_model
  ) %>%
  # as_tibble() %>%
  # group_by(match_id, inning, batting_team, over_inning,inning_match) %>%
  # summarise(total_over = sum(total_runs)) %>%
  granplot(
    gran1 = "ball_over",
    gran2 = "over_match",
    hierarchy_model,
    response = "total_runs",
    plot_type = "quantile"
  )
```

>>>>

# change all of these to gravitas function
VIC <- read.csv("data/VIC2015/Data/demand_VIC.csv")
VIC$Date <- as.Date(VIC$Date, origin = "1899-12-30")

@@

```{r hierarchy, echo=FALSE}
hierarchy_model <- tibble::tibble(units = c("index", "ball", "over", "inning", "match"), 
                                  convert_fct = c(1, 6, 20, 2, 1))
knitr::kable(hierarchy_model, caption = "T20 hierarchy table")
```

@@

```{r read_data, echo=FALSE}

@@

# cricket_tsibble %>% dynamic_create_gran(
#   "ball_over",
#   hierarchy_model
# )

#over_inning    ball_over 
cricket_tsibble %>% granplot("over_inning", "ball_over",
  hierarchy_model,
  response = "total_runs",
  plot_type = "violin"

)

#inning_match   ball_over

cricket_tsibble %>% granplot("inning_match", "ball_over",
  hierarchy_model,
  response = "total_runs"
)

# inning_match   ball_inning

cricket_tsibble %>% granplot("inning_match", "ball_inning",
  hierarchy_model,
  response = "total_runs"
)

# ball_over      over_inning

cricket_tsibble %>% granplot("ball_over", "over_inning",
  hierarchy_model,
  response = "total_runs"
)

# inning_match   over_inning

cricket_tsibble %>% granplot("inning_match", "over_inning",
  hierarchy_model,
  response = "total_runs"
)

# ball_over      over_match

cricket_tsibble %>% granplot("ball_over", "over_match",
  hierarchy_model,
  response = "total_runs"
)

# ball_over      inning_match

cricket_tsibble %>% granplot("ball_over", "over_match",
  hierarchy_model,
  response = "total_runs"
)

cricket_tsibble %>%
  granplot(
    gran1 = "inning_match",
    gran2 = "over_inning",
    hierarchy_model,
    response = "total_runs",
    plot_type = "quantile"
  )
